\section{DATA DESCRIPTION}

In order to ensure the success of our work, we formulate a set of questions and obtain the necessary data using a Google Form. To access the form, please visit: \url{https://forms.gle/VDTpe4S4yUoHkkbG6}

\section*{Personal Information}
\begin{enumerate}
    \item \textit{Name:}
    \item \textit{Age:}
    \item \textit{Gender:}
    \item \textit{Current Employment Status:}
    \item \textit{Profession:}
\end{enumerate}

\section*{Family and Vaccination Status}
\begin{enumerate}[resume]
    \item Number of Heads in Family (Including yourself):
    \item Have you been vaccinated completely against COVID-19?
\end{enumerate}

\section*{Occupational and Activity Engagement}
\begin{enumerate}[resume]
    \item Were you engaged in any occupation / project / institutional activities during specific times?
    \item Were you engaged in those activities mostly from home during specific times?
\end{enumerate}

\section*{Outdoor Activities and Testing}
\begin{enumerate}[resume]
    \item How often did you go outside at the time of Corona?
    \item Had you tested yourself for COVID-19?
    \item Were the results positive?
\end{enumerate}

\section*{Health and Chronic Conditions}
\begin{enumerate}[resume]
    \item Rate the severity of COVID-19 infection on your health ?
    \item Did you have any chronic disease / co-morbidity before COVID-19?
    \item Please rate the change in severity of the chronic disease before and after the pandemic on a scale of $0$ to $5$ (With $0$ being Did Not Change / Not Applicable and $5$ being Reached a Critical Level.)
\end{enumerate}

\section*{Mental Health and Physical Well-being}
\begin{enumerate}[resume]
    \item Have you faced any unusual mental health issues during COVID-19?
    \item Please mention an approximate value for the following quantity (in Kg): Your weight after the pandemic - Your weight before the pandemic (Subtract, negative values may arise.)
\end{enumerate}

\section*{Financial and Medical Impact}
\begin{enumerate}[resume]
    \item Were any of your family members tested positive for COVID-19?
    \item Were there any deaths due to COVID-19 in your family?
    \item Please mention an approximate value for the following quantity (in \textit{INR}): Monthly medical expenses of your family after the pandemic - That before the pandemic (Subtract, negative values may arise.)
\end{enumerate}

\section*{Hygiene Practices and Adherence}
\begin{enumerate}[resume]
    \item Have you used the following items? (\textit{Before/During/After} COVID-19)
    \begin{itemize}
        \item \textit{Sanitizer.}
        \item \textit{Face mask.}
        \item \textit{Head mask.}
        \item \textit{Hand gloves.}
        \item \textit{Face shield.}
    \end{itemize}
    \item Have you followed the mentioned rules/practices?
    \begin{itemize}
        \item \textit{Safe distancing.}
        \item \textit{No touch product acceptance.}
        \item \textit{Washing marketed products thoroughly.}
        \item \textit{Washing hands with soap for a minimum of $20$ sec.}
        \item \textit{Physically exercising.}
    \end{itemize}
\end{enumerate}

\section*{Lifestyle Changes}
\begin{enumerate}[resume]
    \item How much have you depended on the cooked-food delivery system? (Choose the closest answers.)
    \item How have your average screen times (on phone, TV, etc.) been? (Choose the closest answers.)
    \item Considering its severity, if there is another epidemic like COVID-19 within the next $20$ years, do you have any hygiene plans to combat it?
\end{enumerate}

\section*{Perception and Future Preparedness}
\begin{enumerate}[resume]
    \item What has been COVID-19's effect on the growth of education in your family?
    \item Do you have economic backup plans for any upcoming epidemic within the next $20$ years?
    \item How have the following aspects changed in your life after COVID-19?
    \begin{itemize}
        \item \textit{Social interaction.}
        \item \textit{Annual family income.}
        \item \textit{Monthly family expenses.}
        \item \textit{Screen-time.}
        \item \textit{Dependence on the ready-made delivery system.}
    \end{itemize}
    \item Considering the general reluctance to adapt to the new lifestyle during the COVID-19 pandemic, how likely are you to start following the safety rules imposed (by the nationally accepted medical societies), if there is a pandemic in the next $20$ years?
    \item Is there any other experience/changes in your life due to the pandemic that you would wish to share with us? If '\textit{Yes}', please write.
\end{enumerate}